Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-07-31 volunteer-clouds-ieee-ci-si.tex

@@

\begin{figure}[!t]
\centering
\includegraphics[width=2.5in]{myfigure}
\caption{Comparison of time to solution for the baseline system, using a {\tt
    node.js} client, for different population sizes. They only compare
runs in which solution has been found.}
%\label{fig_sim}
%\end{figure}
First we establish the baseline performance by running the
evolutionary algorithm in a desktop client written using {\sf NodEO},
the node.js evolutionary algorithm library. This experiment tries to
find the solution to the 40-trap function with parameters $l=4, a=1,
b=2, z=3$, a population size equal 512, which was found in previous
experiments to be the correct one for finding the solution 95\% of the
time. The algorithm was run until the solution (a string with all
ones) was found or five millions evaluations had been performed. It
took around a minute, on average, that is $68.9694$ seconds, to
perform the fifty runs. In this experiment only 33, that is, 66\% were
successful. The experiments were repeated for population $p=1024$,
with success rate upgraded to 100\%. Results for these two experiments
are shown in Figure \ref{fig:baseline}.

>>>>

Figure \ref{fig:system} describes the system.

\begin{figure}[!t]
\centering
\includegraphics[width=4in]{img/system.pdf}
\caption{Description of the used system. Clients execute a JS EA in the browser. Every 100 generations it sends the best individual and receives a random one from the server.}
\label{fig:system}
\end{figure}

@@

\begin{figure}[!t]
\centering
%\includegraphics[width=2.5in]{myfigure}
\caption{Comparison of time to solution for the baseline system, using a {\tt
    node.js} client, for different population sizes. They only compare
runs in which solution has been found.}
\label{fig_sim}
\end{figure}
First we establish the baseline performance by running the
evolutionary algorithm in a desktop client written using {\sf NodEO},
the node.js evolutionary algorithm library. This experiment tries to
find the solution to the 40-trap function with parameters $l=4, a=1,
b=2, z=3$, a population size equal 512, which was found in previous
experiments to be the correct one for finding the solution 95\% of the
time. The algorithm was run until the solution (a string with all
ones) was found or five millions evaluations had been performed. It
took around a minute, on average, that is $68.9694$ seconds, to
perform the fifty runs. In this experiment only 33, that is, 66\% were
successful. The experiments were repeated for population $p=1024$,
with success rate upgraded to 100\%. Results for these two experiments
are shown in Figure \ref{fig:baseline}.
